Minimizing post-shock forecasting error using disparate information

### 2020-08-06 manuscript/manuscript.tex
addressed Forrest and Karl Oskar edits; I left a few small comments

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for the time series data that have undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock effects estimators were constructed for minimizing average forecast risk. We proposed risk-reduction propositions providing conditions when our methodology works and estimators for risk-reduction quantities. Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock forecasts before the post-shock response is observed. The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well. Leave-one-out cross validation is proposed to estimate correctness of risk-reduction propositions, prospectively informing users of the probabilities that this prospective evaluation is in line with the reality. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

We study the post-shock forecasting problem in the context of additive shock effects in linear autoregressive models. In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed. The researcher must therefore move beyond the modeling paradigm under which he or she was previously working  to accommodate this new shock \citep{monti2008forecast, svensson2005monetary}. One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}. Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}. On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting context provided that the shock effects are all thought to arise from a similar data generating process. For further differences of assumptions on shocks, our methodology allows for \emph{unprecedented} shocks and no observation of past shocks.

In our methodological framework, the researcher creates a synthetic panel of disparate time series which have undergone similar structural shocks in the past. Construction of the donor pool that forms this synthetic panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}. As in SCM, care is needed when forming the donor pool of disparate time series. However, there are key differences between our framework and SCM. We assume that the disparate time series are independent from the time series under study before the timing of the shock. We also assume that the shock effects for each disparate time series are independent realizations from some unknown distribution.

We estimate the shock effects that are present in the disparate time series for which post-shock responses are observed. We then aggregate these estimated shock effects and use this aggregated estimate as an estimator for the shock effect in the time series of interest. This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest. Shock effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}. The context in \cite{clements2019measuring} allowed for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}. There is no consistency guarantee here. In our context, the yet to observed shock effect of interest is a realization from a random process that can only be partially explained by the realizations of the disparate time series. Therefore, the shock effect of interest can not be estimated consistently.

@@

In this section, we will describe the assumed dynamic panel models for which 
post-shock aggregated estimators are provided. The basic structures of these models 
are the same, the differences between them lie in the setup of the shock effect 
distribution.

@@

\subsection{Forecast}
\label{forecast}
In this section we show how post-shock aggregate estimators improve upon standard 
forecasts that do not account for the shock effect.
%The interest of this study lies in comparing how consideration of shock effects 
%improves the prediction. 
More formally, we will consider the following candidate forecasts: 
\begin{align*}
  &\text{Forecast 1}: \hat y_{1,T_1^*+1}^1 = \hat\eta_1 
    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
    , \\
  &\text{Forecast 2}: \hat y_{1,T_1^*+1}^2 = \hat\eta_1 
    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
    + \hat{\alpha},
\end{align*}
where $\hat\eta_1$, $\hat\phi_1$, and $\hat\theta_1$ are all ordinary least squares (OLS) estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively, and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$. 
The first forecast ignores the presence of $\alpha_1$ while the second forecast 
incorporates an estimate of $\alpha_1$ that is obtained from the other independent forecasts under study. 
%Under $\mc{M}_1$ (Section \ref{modelsetup}), $\E{\alpha_1} = \mu_{\alpha}$.

@@

We use similar notation as that in \cite{abadie2010synthetic} to motivate our weighted-adjustment estimator. Consider a $\mbf{W} \in \R^n$ weight vector 
$\mbf{W}=(w_2, \ldots, w_{n+1})'$, where $w_i\in [0,1]$ for all 
$i = 2, \ldots, n+1$. Construct
\begin{align*}
 \mbf{X}_1 = \mbf{x}_{1, T_1^*+1}',
  \quad  
  \mbf{X} = \begin{pmatrix}
    \mbf{x}_{2, T_2^*+1}' \\
    \vdots \\
    \mbf{x}_{n+1, T_{n+1}^*+1}'
  \end{pmatrix},
  \quad \text{and} \quad 
  \hat{\mbf{X}}_1(\mbf{W}) 
    = \mbf{W}'\mbf{X},
\end{align*}
where $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{1 \times p}$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon 1_n'\mbf{W} = 1 \}$. 
Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)'$ such that
\begin{align}
 \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*),  \quad i.e., \quad \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
\end{align}
 Notice that $\mbf{W}^*$ exists as long as $\mbf{X}_1$ falls in the convex hull of 
 \begin{align*}
   \left\{ \mbf{x}_{2, T_2^*+1}', \ldots, \mbf{x}_{n+1, T_{n+1}^*+1}' \right\}.
 \end{align*}
%It is a reasonable assumption that the pool of time series that we are considering 
%should be similar to the time series of interest. 
Our weighted-adjustment estimator will therefore perform well when the pool of 
disparate time series posses similar covariates to the time series for which 
no post-shock responses are observed. We compute $\mbf{W}^*$ as
\begin{align}
  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})}_{p}. 
  \label{W}
\end{align}
%which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
%still hold approximately 
and that weighted-adjustment estimation techniques of this form are not 
appropriate when the fit is poor. 
Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist. %Relying on this weight, 
%we are mainly interested in constructing the following adjustment estimator:
Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
  \begin{align*}
    \hat{\alpha}_{\rm wadj} = \sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i
    \quad \text{ for } \quad \mbf{W}^* = \begin{pmatrix}
      w^*_2 & \cdots & w^*_{n+1}
    \end{pmatrix}'.
  \end{align*}
 %Different from \citet{abadie2010synthetic}, our construction customizes synthetic control methods to the setting of AR(1) model. To be more specific, notice that (\ref{SCM}) implicitly uses the covariates at $T_*$ the shock-time and $T_*-1$ the time point just before the shock. This model somehow accounts for the impact of past information on the shock effects. 
 We further define
\begin{align*}
  \mathbf{V} = (\mathbf{x}_{2, T_2^*+1}, \ldots,\mathbf{x}_{n+1, T_{n+1}^*+1}).
\end{align*}
\begin{prop}
  \label{uniqueness} If $\mathbf{V}$ has full rank and it exists some $\mathbf{W}$ satisfies (\ref{SCM}), the solution to  (\ref{W}) is unique.
\end{prop} 
Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.  Note that $\mathbf{V}$ is $p \times n$. Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $p \geq n$. However, when $p < n$, $\mathbf{W}^*$ may not be unique. If it exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $p < n$, there are infinitely many solutions to (\ref{SCM}).  The issue of non-uniqueness is further discussed in Section \ref{varbootstrap}.

@@

\section{Forecasting Conoco Phillips stock in the presence of shocks}
\label{forecasting}
In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus recession. Specific interest is in predictions made after March 6, 2020, the Friday before the stock market crash on March 9, 2020. We will detail how we combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price that would be made without adjustments for the shock. %Section \ref{background} provides the justification for the first three steps. Section \ref{results} discusses the result of our forecast.

@@

Conoco Phillips is chosen for this analysis because it is a large oil and gas resources company \citep{conocowhatwedo}. %and with a relatively recent initial public offering \citep{conocohist}. 
Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices \citep{he2010global}, and our chosen time frame represents the onset of a significant economic down turn, coupled with a Russia and OPEC battle for global oil price control on the Sunday before trading resumes on Monday, March 9th \citep{sukhankin2020russian}. Furthermore, fear and action in response to the coronavirus pandemic began to uptick dramatically between Friday, March 6th and Monday, March 9th. Major events include the SXSW festival being cancelled as trading closed on March 6th \citep{wang2020impact}. New York declared a state of emergency on March 7th \citep{nygov}, and by Sunday, March 8th, eight states have declared a state of emergency \citep{alonso2020state} while Italy placed 16 million people in quarantine \citep{sjodin2020only}.

Economic indicators forecasted our recession before the coronavirus pandemic began. The current recession followed an inversion of the yield curve that first happened back in March, 2019 \citep{tokic2019yield}. An inversion of the yield curve is an event that signals likely recessions \citep{andolfatto2018yield, bauer2018economic}. In this analysis we investigate the performance of oil companies in previous recessions that followed an inversion of the yield curve to obtain a suitable Conoco Phillips donor pool for estimating the March 9th shock effect on Conoco Phillips oil stock. We also consider previous OPEC oil supply shocks \citep{mensi2014opec}. We will borrow from the literature on oil price forecasting to establish appropriate time horizons and forecasting models. Recessions that occurred before 1973 are disregarded since oil price forecasts cannot be represented by standard time series models before 1973 \citep{alquist2013forecasting}. In this analysis we make the following considerations:

\begin{enumerate}
\item[(1)] {\bf AR(1) model and time window}. We will use an AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}. We will consider 30 pre-shock trading days and we will forecast the immediate shock effect and the shock effect over a future five trading day window. All estimates will be adjusted for inflation. The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects. All the parameters are estimated using OLS.
\item[(2)] {\bf Selection of covariates}. We perform our analyses incorporating daily S\&P 500 index prices and West Texas Intermediate (WTI) crude oil prices as covariates. 
\item[(3)] {\bf Construction of donor pool}. Our donor pool  consists of Conoco Phillips shock effects observed on March 14, 2008, several events in September, 2008, and November 27, 2014. The first two shock effects were observed during recessions that were predicated by an inversion of the yield curve \citep{bauer2018economic}, and the third was an OPEC induced supply side shock effect \citep{huppmann2015opec}. The reasons for those three shocks are:
  \begin{enumerate}
  \item On March 14, 2008, Bear Stearns was verging on bankruptcy from what its officials described as a sudden liquidity squeeze related to its large exposure to devalued mortgage-backed securities. On that day, it also received word that it was getting an unprecedented loan from the Federal Reserve System, this decision was unprecedented: never before had the Fed committed to ``bailing out'' a financial entity that was not a commercial bank. The day of the announcement, the stocks of other major Wall Street firms tumbled (including Conoco Phillips). These concerns then spilled over into the broader universe of stocks \citep{shorter2008bear}. %In heavy trading on Tuesday, March 18, the firm’s share price closed at \$5.91.
  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets. The political, economic, social or environmental events may coincide with these shocks \citep{ewing2013volatility}. Notable shock effects followed the placement of Fannie May and Freddie Mac in conservatorship on September 7th (shock effect on the 8th), Lehman Brothers filing for bankruptcy on September 15th, and the Office of Thrift Supervision closes Washington Mutual Bank on September 25th \citep{dwyer2009financial, longstaff2010subprime}.
  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}. During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors. During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}. 
  \end{enumerate}
\end{enumerate}

@@

The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}=-5.348$, $\hat{\alpha}_{\rm wadj}= -5.761$, and $\hat{\alpha}_{\rm IVW}=-5.290$. Using the bootstrap procedure $\mc{B}_f$, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}. The estimated bootstrap variances for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  are 0.567, 0.499, and 1.006, respectively. Plugging these estimates into conditions in Section \ref{properties} yields: (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $32.452$, $32.690$, and $31.960$, respectively. We verify the consistency of the result yielded by risk-reduction propositions with the reality as below.

@@

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, and they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects. 
The unadjusted forecast has an RMSE of 9.870 dollars whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ have  RMSE of $4.522$, $4.109$, and $3.581$ dollars, respectively. 
Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without. Moreover, the risk-reduction quantities are consistent with the reality as well.

The phenomenon that the true shock effect is not recovered by $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ can be due to that the donor pool is not constructed to be similar enough to the time series of interest. The shock(s) on March 9, 2020 is(are) in the midst of the COVID-19 pandemic and oil production volatility. It is difficult to find available stock market time series data that were generated under a similar setting.

>>>>

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for the time series data that have undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock effects estimators were constructed for minimizing average forecast risk. We proposed risk-reduction propositions providing conditions when our methodology works. Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential prospective success of post-shock forecasts. %The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well. 
    Leave-one-out cross validation is proposed to estimate correctness of risk-reduction propositions, prospectively informing users of the probabilities that this prospective evaluation is in line with the reality. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

We study the post-shock forecasting problem in the context of additive shock effects in linear autoregressive models. In this post-shock forecasting setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed. In this setting, the additive shock effect is a random effect that is parameterized in the autoregressive model. The shock effect is then estimated using ordinary least squares (OLS). The researcher must move beyond the modeling paradigm that they were previously working under to accommodate this new shock effect \citep{monti2008forecast, svensson2005monetary}. One method for estimating the shock effect is to produce a conditional point forecast where a sequence of non-zero future structural shocks are conditioned upon and estimated \citep{baumeister2014real}. Such conditional point forecasts are appropriate when the shock sequence considered is within the range of historical experience \citep{kilian2017structural}. On the other hand, our methodology allows for the inclusion of outside data sources and covariates into this conditional forecasting context provided that the shock effects are all thought to arise from a similar data generating process. For further differences of assumptions on shocks, our methodology allows for \emph{unprecedented} shocks and no observation of past shocks.

In our methodological framework, the researcher creates a synthetic panel of disparate time series which have undergone similar structural shocks in the past. Construction of the donor pool that forms this synthetic panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}. As in SCM, care is needed when forming the donor pool of disparate time series. However, there are key differences between our framework and SCM. We assume that the disparate time series are independent from the time series under study before the timing of the shock {\bf Jilei, can weaken this assumption?}. We also assume that the shock effects for each disparate time series are independent realizations from some unknown distribution.

We estimate the shock effects that are present in the disparate time series for which post-shock responses are observed. We then aggregate these estimated shock effects and use this aggregated estimate as an estimator for the shock effect in the time series of interest. This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest. Shock effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}. The context in \cite{clements2019measuring} allowed for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}. In our context, the yet to observed shock effect of interest is a random effect, and we can only partially estimate features of the random effect distribution using the disparate time series.

@@

In this section, we will describe the assumed dynamic panel models for which 
post-shock aggregated estimators are provided. The basic structures of these models 
are the same for all time-series in the analysis, the differences between them lie in the setup of the shock effect distribution.

@@

\subsection{Forecast}
\label{forecast}
In this section we show how post-shock aggregate estimators improve upon standard 
forecasts that do not account for the shock effect.
%The interest of this study lies in comparing how consideration of shock effects 
%improves the prediction. 
More formally, we will consider the following candidate forecasts: 
\begin{align*}
  &\text{Forecast 1}: \hat y_{1,T_1^*+1}^1 = \hat\eta_1 
    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
    , \\
  &\text{Forecast 2}: \hat y_{1,T_1^*+1}^2 = \hat\eta_1 
    + \hat\phi_1 y_{1,T_1^*} + \hat\theta_1'\x_{1,T_1^*+1} 
    + \hat{\alpha},
\end{align*}
where $\hat\eta_1$, $\hat\phi_1$, and $\hat\theta_1$ are all OLS estimators of $\eta_1$, $\phi_1$, and $\theta_1$, respectively, and $\hat{\alpha}$ is some form of estimator for the shock effect of time series of interest, i.e., $\alpha_1$. 
The first forecast ignores the presence of $\alpha_1$ while the second forecast 
incorporates an estimate of $\alpha_1$ that is obtained from the other independent forecasts under study. 
%Under $\mc{M}_1$ (Section \ref{modelsetup}), $\E{\alpha_1} = \mu_{\alpha}$.

@@

We use similar notation as that in \cite{abadie2010synthetic} to motivate our weighted-adjustment estimator. Consider a $\mbf{W} \in \R^n$ weight vector 
$\mbf{W}=(w_2, \ldots, w_{n+1})'$, where $w_i\in [0,1]$ for all 
$i = 2, \ldots, n+1$. Construct
\begin{align*}
 \mbf{X}_1 = \mbf{x}_{1, T_1^*+1}',
  \quad  
  \mbf{X} = \begin{pmatrix}
    \mbf{x}_{2, T_2^*+1}' \\
    \vdots \\
    \mbf{x}_{n+1, T_{n+1}^*+1}'
  \end{pmatrix},
  \quad \text{and} \quad 
  \hat{\mbf{X}}_1(\mbf{W}) 
    = \mbf{W}'\mbf{X},
\end{align*}
where $\mbf{X}_1,\hat{\mbf{X}}_1(\mbf{W}) \in \R^{1 \times p}$. Define $\mc{W}=\{\mbf{W}\in [0,1]^n \colon 1_n'\mbf{W} = 1 \}$. 
Suppose there exists $\mbf{W}^*\in \mc{W}$ with 
$\mbf{W}^*=(w_2^*, \ldots, w_{n+1}^*)'$ such that
\begin{align}
 \mbf{X}_1=\hat{\mbf{X}}_1(\mbf{W}^*),  \quad i.e., \quad \mbf{x}_{1, T_1^*+1} = \sum_{i=2}^{n+1} w_i^*\mbf{x}_{i, T_i^*+1}.\label{SCM}
\end{align}
 Notice that $\mbf{W}^*$ exists as long as $\mbf{X}_1$ falls in the convex hull of 
 \begin{align*}
   \left\{ \mbf{x}_{2, T_2^*+1}', \ldots, \mbf{x}_{n+1, T_{n+1}^*+1}' \right\}.
 \end{align*}
{\bf Jilei, can you add clarity to this point? It is hard to see why this works on the first viewing.}
%It is a reasonable assumption that the pool of time series that we are considering 
%should be similar to the time series of interest. 
Our weighted-adjustment estimator will therefore perform well when the pool of 
disparate time series posses similar covariates to the time series for which 
no post-shock responses are observed. We compute $\mbf{W}^*$ as
\begin{align}
  \mbf{W}^* = \argmin_{\mbf{W}\in \mc{W}} \norm{\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W})}_{p}. 
  \label{W}
\end{align}
%which is a more general form of $\mbf{W}^*$ for the case when $\mbf{X}_1$ does not fall in the convex hull of (\ref{convexhull}). 
\cite{abadie2010synthetic} commented that we can select $\mbf{W}^*$ 
so that (\ref{SCM}) holds approximately %so that the property of $\mbf{W}^*$ should 
%still hold approximately 
and that weighted-adjustment estimation techniques of this form are not 
appropriate when the fit is poor. 
Note that $\mbf{W}^*$ is not random since the covariates are assumed to be fixed. Since $\mc{W}$ is a closed and bounded subset of $\reals^n$,  $\mc{W}$ is compact. Because the objective function 
is continuous in $\mbf{W}$, $\mbf{W}^*$ will always exist. %Relying on this weight, 
%we are mainly interested in constructing the following adjustment estimator:
Our weighted-adjustment estimator for the shock effect $\alpha_1$ is
  \begin{align*}
    \hat{\alpha}_{\rm wadj} = \sum_{i=2}^{n+1} w_i^*\hat{\alpha}_i
    \quad \text{ for } \quad \mbf{W}^* = \begin{pmatrix}
      w^*_2 & \cdots & w^*_{n+1}
    \end{pmatrix}'.
  \end{align*}
 %Different from \citet{abadie2010synthetic}, our construction customizes synthetic control methods to the setting of AR(1) model. To be more specific, notice that (\ref{SCM}) implicitly uses the covariates at $T_*$ the shock-time and $T_*-1$ the time point just before the shock. This model somehow accounts for the impact of past information on the shock effects. 
 We further define
\begin{align*}
  \mathbf{V} = (\mathbf{x}_{2, T_2^*+1}, \ldots,\mathbf{x}_{n+1, T_{n+1}^*+1}).
\end{align*}
\begin{prop}
  \label{uniqueness} If $\mathbf{V}$ has full rank and it exists some $\mathbf{W}$ satisfies (\ref{SCM}), the solution to  (\ref{W}) is unique.
\end{prop} 
Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.  Note that $\mathbf{V}$ is $p \times n$. Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $p \geq n$. However, when $p < n$, $\mathbf{W}^*$ may not be unique. If it exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $p < n$, there are infinitely many solutions to (\ref{SCM}).  The issue of non-uniqueness is further discussed in Section \ref{varbootstrap}.

@@

\section{Forecasting Conoco Phillips stock in the presence of shocks}
\label{forecasting}

We demonstrate our post-shock forecasting methodology on a time series of Conoco Phillips share prices after the occurrence of a structural shock. Conoco Phillips is a large oil and gas resources company \citep{conocowhatwedo}. The particular post-shock response that we predict happened after trading ended on Friday March 6th, 2020 and before trading began on Monday March 9th, 2020. It is reasonable that the timing of this shock is known, several events occurred over the trading weekend which had an impact on stock markets and the oil markets. For example, Russia and OPEC began a battle for global oil price control on Sunday, March 8th \citep{sukhankin2020russian}, and several US states began declaring state of emergencies in response to the evolving coronavirus pandemic \citep{nygov, alonso2020state}. In this analysis we make the following design considerations:

%In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus recession. Specific interest is in predictions made after March 6, 2020, the Friday before the stock market crash on March 9, 2020. We will detail how we combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price that would be made without adjustments for the shock. %Section \ref{background} provides the justification for the first three steps. Section \ref{results} discusses the result of our forecast.

@@

%Conoco Phillips is chosen for this analysis because it is a large oil and gas resources company \citep{conocowhatwedo}. %and with a relatively recent initial public offering \citep{conocohist}. 
%Focus on the oil sector is because oil prices have been shown to exhibit a cointegrating behavior with economic indices \citep{he2010global}, and our chosen time frame represents the onset of a significant economic down turn, coupled with a Russia and OPEC battle for global oil price control on the Sunday before trading resumes on Monday, March 9th \citep{sukhankin2020russian}. Furthermore, fear and action in response to the coronavirus pandemic began to uptick dramatically between Friday, March 6th and Monday, March 9th. Major events include the SXSW festival being cancelled as trading closed on March 6th \citep{wang2020impact}. New York declared a state of emergency on March 7th \citep{nygov}, and by Sunday, March 8th, eight states have declared a state of emergency \citep{alonso2020state} while Italy placed 16 million people in quarantine \citep{sjodin2020only}.

%Economic indicators forecasted our recession before the coronavirus pandemic began. The current recession followed an inversion of the yield curve that first happened back in March, 2019 \citep{tokic2019yield}. An inversion of the yield curve is an event that signals likely recessions \citep{andolfatto2018yield, bauer2018economic}. In this analysis we investigate the performance of oil companies in previous recessions that followed an inversion of the yield curve to obtain a suitable Conoco Phillips donor pool for estimating the March 9th shock effect on Conoco Phillips oil stock. We also consider previous OPEC oil supply shocks \citep{mensi2014opec}. We will borrow from the literature on oil price forecasting to establish appropriate time horizons and forecasting models. Recessions that occurred before 1973 are disregarded since oil price forecasts cannot be represented by standard time series models before 1973 \citep{alquist2013forecasting}.

\begin{enumerate}
\item[(1)] {\bf Selection of model}. We will use an AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}.  For these reasons, we will consider 30 pre-shock trading days and we will forecast the immediate shock effect. All estimates will be adjusted for inflation. The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects. All the parameters are estimated using OLS.
\item[(2)] {\bf Selection of covariates}. We perform our analyses incorporating daily S\&P 500 index prices and West Texas Intermediate (WTI) crude oil prices as covariates. 
\item[(3)] {\bf Construction of donor pool}. Our donor pool consists of Conoco Phillips shock effects observed in the past. We consider shock effects which occurred on March 14, 2008, several days in September, 2008, and November 27, 2014. The first sets of shock effects were observed during recessions that possessed similar characteristics to the current recession. In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}. These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie Mac in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}. The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}. %The reasons for those three shocks are.
%  \begin{enumerate}
%  \item On March 14, 2008, Bear Stearns was verging on bankruptcy from what its officials described as a sudden liquidity squeeze related to its large exposure to devalued mortgage-backed securities. On that day, it also received word that it was getting an unprecedented loan from the Federal Reserve System, this decision was unprecedented: never before had the Fed committed to ``bailing out'' a financial entity that was not a commercial bank. The day of the announcement, the stocks of other major Wall Street firms tumbled (including Conoco Phillips). These concerns then spilled over into the broader universe of stocks \citep{shorter2008bear}. %In heavy trading on Tuesday, March 18, the firm’s share price closed at \$5.91.
%  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets. The political, economic, social or environmental events may coincide with these shocks \citep{ewing2013volatility}. Notable shock effects followed the placement of Fannie May and Freddie Mac in conservatorship on September 7th (shock effect on the 8th), Lehman Brothers filing for bankruptcy on September 15th, and the Office of Thrift Supervision closes Washington Mutual Bank on September 25th \citep{dwyer2009financial, longstaff2010subprime}.
%  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}. During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors. During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}. 
%  \end{enumerate}
\end{enumerate}

@@

The resulting shock effect estimates are $\hat{\alpha}_{\rm adj}=-5.348$, $\hat{\alpha}_{\rm wadj}= -5.761$, and $\hat{\alpha}_{\rm IVW}=-5.290$. Using the bootstrap procedure $\mc{B}_f$, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}. The estimated bootstrap variances for $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  are 0.567, 0.499, and 1.006, respectively. %Plugging these estimates into conditions in Section \ref{properties} yields: (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $32.452$, $32.690$, and $31.960$, respectively. 
We verify the consistency of the result yielded by risk-reduction propositions with the reality as below.

@@

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, and they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects. 
The unadjusted forecast misses the post-shock response by 9.870 dollars whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ misses by $4.522$, $4.109$, and $3.581$ dollars, respectively. 
%Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without. Moreover, the risk-reduction quantities are consistent with the reality as well. 
The true shock effect is not fully recovered by $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$. This may be a result of a poorly constructed donor pool. The shock on March 9th, 2020 is in the midst of the COVID-19 pandemic and oil production volatility. It is difficult to find available stock market time series data that were generated under a similar setting. In any event, the shock on March 9th, 2020 was the largest price shock to Conoco Phillips shares by a wide margin, even after adjusting for inflation.
